Lesson 5
========================================================

### Multivariate Data
Notes:

***

### Moira Perceived Audience Size Colored by Age
Notes:

***

### Third Qualitative Variable
Notes:

```{r Third Qualitative Variable}
library(ggplot2)
pf<- read.csv('E:/data analysis/class/EDA_Course_Materials/lesson3/pseudo_facebook.tsv',sep='\t')
ggplot(aes(x = gender, y = age),
       data = subset(pf, !is.na(gender))) + geom_boxplot()+
  stat_summary(fun.y=mean, geom='point', shape=4)

library(ggplot2)
ggplot(aes(x=age,y=friend_count),data=subset(pf, !is.na(gender)))+
  geom_line(aes(color=gender),stat = 'summary',fun.y= median)

library(dplyr)
pf.fc_by_age_gender<- pf %>%
  filter(!is.na(gender)) %>%
  group_by(age, gender) %>%
  summarise(mean_friend_count=mean(friend_count),
            median_friend_count=median(friend_count),
            n=n()) %>%
  ungroup() %>%
  arrange(age)
```

***

### Plotting Conditional Summaries
Notes:

```{r Plotting Conditional Summaries}
ggplot(aes(x=age,y=median_friend_count),data=pf.fc_by_age_gender)+
  geom_line(aes(color=gender))
```

***

### Thinking in Ratios
Notes:

***

### Wide and Long Format
Notes:

***

### Reshaping Data
Notes:

```{r}
library(reshape2)
pf.fc_by_age_gender.wide<- dcast(pf.fc_by_age_gender,
                                 age~gender,
                                 value.var = 'median_friend_count')

head(pf.fc_by_age_gender.wide)
```


***

### Ratio Plot
Notes:

```{r Ratio Plot}
ggplot(aes(x=age, y=female/male),data=pf.fc_by_age_gender.wide)+
  geom_line()+
  geom_hline(yintercept = 1,alpha=0.3, linetype =2)
```

***

### Third Quantitative Variable
Notes:

```{r Third Quantitative Variable}
pf$year_joined <- floor(2014- pf$tenure/365)
summary(pf$year_joined)
table(pf$year_joined)
```

***

### Cut a Variable
Notes:

```{r Cut a Variable}
pf$year_joined.bucket <- cut(pf$year_joined,
                             c(2004,2009,2011,2012,2014))
```

***

### Plotting it All Together
Notes:

```{r Plotting it All Together}
library(ggplot2)
ggplot(aes(x=age, y=friend_count),data=subset(pf, !is.na(year_joined.bucket)))+
  geom_line(aes(color= year_joined.bucket), stat='summary',fun.y=median)
```

***

### Plot the Grand Mean
Notes:

```{r Plot the Grand Mean}
library(ggplot2)
ggplot(aes(x=age, y=friend_count),data=subset(pf, !is.na(year_joined.bucket)))+
  geom_line(aes(color= year_joined.bucket), stat='summary',fun.y=mean)+
  geom_line(stat='summary',fun.y=mean, linetype=2)
```

***

### Friending Rate
Notes:

```{r Friending Rate}
with(subset(pf, tenure>=1), summary(friend_count/tenure))
```

***

### Friendships Initiated
Notes:

What is the median friend rate?

What is the maximum friend rate?

```{r Friendships Initiated}
ggplot(aes(x=tenure,y=friendships_initiated/tenure),
       data=subset(pf, tenure>=1))+
       geom_line(aes(color=year_joined.bucket))
```

***

```{r}
library(ggplot2)
ggplot(aes(x=7*round(tenure/7),y=friendships_initiated/tenure),
       data=subset(pf, tenure>=1))+
  geom_smooth(aes(color=year_joined.bucket))
```


```{r}
yo <- read.csv('E:/data analysis/class/EDA_Course_Materials/lesson5/yogurt.csv')
str(yo)

yo$id <- factor(yo$id)
str(yo)

qplot(data=yo, x=price, fill=I('#F79420'))
```


### Bias-Variance Tradeoff Revisited
Notes:

```{r Bias-Variance Tradeoff Revisited}

ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = mean)

ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 30 * round(tenure / 30), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 90 * round(tenure / 90), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

```

***

### Sean's NFL Fan Sentiment Study
Notes:

***

### Introducing the Yogurt Data Set
Notes:

***

### Histograms Revisited
Notes:

```{r Histograms Revisited}
summary(yo)
length(unique(yo$price))
table(yo$price)
```

***

### Number of Purchases
Notes:

```{r Number of Purchases}
yo <- transform(yo, all.purchases= yo$strawberry + yo$blueberry + yo$pina.colada + yo$plain + yo$mixed.berry)

summary(yo$all.purchases)
```

***

### Prices over Time
Notes:

```{r Prices over Time}
ggplot(aes(x=time, y=price), data=yo)+
  geom_jitter(alpha=1/4, shape=21, fill=I('#F79420'))
```

***

### Sampling Observations
Notes:

***

### Looking at Samples of Households

```{r Looking at Sample of Households}
set.seed(4230)
sample.ids<- sample(levels(yo$id),16)

library(ggplot2)
ggplot(aes(x=time, y=price),
       data = subset(yo, id%in% sample.ids))+
  facet_wrap(~id)+
  geom_line()+
  geom_point(aes(size=all.purchases), pch=1)


```

***

### The Limits of Cross Sectional Data
Notes:
```{r}
library(ggplot2)
library(GGally)
theme_set(theme_minimal(20))

set.seed(1836)
pf_subset<- pf[,c(2:7)]
names(pf_subset)
ggpairs(pf_subset[sample.int(nrow(pf_subset),1000),])
```

***

### Many Variables
Notes:

***

### Scatterplot Matrix
Notes:

***

### Even More Variables
Notes:

***

### Heat Maps
Notes:

```{r}
nci <- read.table("E:/data analysis/class/EDA_Course_Materials/lesson5/nci.tsv")
colnames(nci) <- c(1:64)
```

```{r}
library(reshape2)
nci.long.samp <- melt(as.matrix(nci[1:200,]))
names(nci.long.samp) <- c("gene", "case", "value")
head(nci.long.samp)

library(ggplot2)
ggplot(aes(y = gene, x = case, fill = value),
  data = nci.long.samp) +
  geom_tile() +
  scale_fill_gradientn(colours = colorRampPalette(c("blue", "red"))(100))
```


***

### Analyzing Three of More Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

