Lesson 4
========================================================

***

### Scatterplots and Perceived Audience Size
Notes:

***
```{r}
pf<- read.csv('E:/data analysis/class/EDA_Course_Materials/lesson3/pseudo_facebook.tsv', sep = '\t')
```

### Scatterplots
Notes:

```{r Scatterplots}
qplot(x=age, y=friend_count, data=pf)

ggplot(aes(x=age, y=friend_count),data=pf)+
  geom_point()+
  xlim(13,90)
```

***

#### What are some things that you notice right away?
Response:

***

### ggplot Syntax
Notes:

```{r ggplot Syntax}

```

***

### Overplotting
Notes:

```{r Overplotting}
ggplot(aes(x=age, y=friend_count),data=pf)+
  geom_jitter(alpha=1/20)+
  xlim(13,90)
```

#### What do you notice in the plot?
Response:

***

### Coord_trans()
Notes:

```{r Coord_trans()}
ggplot(aes(x=age, y=friend_count),data=pf)+
  geom_point(alpha=1/20)+
  xlim(13,90)+
  coord_trans(y='sqrt')
```

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r}
ggplot(aes(x=age, y=friendships_initiated),data=pf)+
  geom_point(alpha=1/20)+
  xlim(13,90)+
  coord_trans(y='sqrt')

```

#### What do you notice?

***

### Alpha and Jitter
Notes:

```{r Alpha and Jitter}

```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:

```{r Conditional Means}
library(dplyr)
age_groupys <- group_by(pf,age)
pf.fc_by_age <- summarise(age_groupys,
          friend_count_mean=mean(friend_count),
          friend_count_median=median(friend_count),
          n=n())
pf.fc_by_age <- arrange(pf.fc_by_age)

head(pf.fc_by_age)
library(ggplot2)
ggplot(aes(x=age,y=friend_count_mean),data=pf.fc_by_age)+
  geom_line()

```

Create your plot!

```{r Conditional Means Plot}

```

***

### Overlaying Summaries with Raw Data
Notes:


### Correlation on Subsets
Notes:
```{r correlation}
cor.test(pf$age,pf$friend_count,method = 'pearson')
with(pf,cor.test(age,friend_count,method = 'pearson'))
```




```{r}
library(ggplot2)
ggplot(aes(x=age,y=friend_count),data=pf)+
  coord_cartesian(xlim = c(13, 90))+
  geom_point(alpha=0.05,
             position = position_jitter(h=0),
             color='orange')+
  coord_trans(y='sqrt')+
  geom_line(stat='summary',fun.y=mean)+
  geom_line(stat = 'summary',fun.y=quantile,fun.args = list(probs = .1),linetype=2,color='blue')+
  geom_line(stat='summary',fun.y=quantile,fun.args = list(probs = .9),linetype=2,color='red')
```





```{r Correlation on Subsets}
with(subset(pf,age<70), cor.test(age, friend_count,method = 'spearman'))
```

***

### Correlation Methods
Notes:

***

## Create Scatterplots
Notes:

```{r}
library(ggplot2)
ggplot(aes(x=www_likes_received,y=likes_received),data=pf)+
  geom_point()

```

***

### Strong Correlations
Notes:

```{r Strong Correlations}
ggplot(aes(x=www_likes_received,y=likes_received),data=pf)+
  geom_point()+
  xlim(0,quantile(pf$www_likes_received,0.95))+
  ylim(0,quantile(pf$likes_received,0.95))+
  geom_smooth(method='lm',color='red')

```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r strong Correlation}
cor.test(pf$www_likes,pf$likes_received)
```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
install.packages('alr3')
library(alr3)
```

Create your plot!

```{r Temp vs Month}
ggplot(data=Mitchell,aes(x=Month,y=Temp))+
  geom_point()
```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.

b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}

```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}

```

***

### A New Perspective

What do you notice?
Response:

Watch the solution video and check out the Instructor Notes!
Notes:

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}
library(dplyr)
pf$age_with_month <- pf$age+(12-pf$dob_month)/12
month_groups <- group_by(pf, age_with_month)
pf.fc_by_age_months <- summarise(month_groups,
                 friend_count_mean=mean(friend_count),
                 friend_count_median=median(friend_count),
                 n=n())
pf.fc_by_age_months <- arrange(pf.fc_by_age_months)

head(pf.fc_by_age_months)

ggplot(aes(x=age_with_month,y=friend_count_mean),data=pf.fc_by_age_months)+
  geom_line()

```

***

### Age with Months Means

```{r Age with Months Means}

```

Programming Assignment
```{r Programming Assignment}

```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}
library(dplyr)
pf$age_with_month <- pf$age+(12-pf$dob_month)/12
month_groups <- group_by(pf, age_with_month)
pf.fc_by_age_months <- summarise(month_groups,
                 friend_count_mean=mean(friend_count),
                 friend_count_median=median(friend_count),
                 n=n())
pf.fc_by_age_months <- arrange(pf.fc_by_age_months)

head(pf.fc_by_age_months)

ggplot(aes(x=age_with_month,y=friend_count_mean),data=subset(pf.fc_by_age_months,age_with_month<71))+
  geom_line()
```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}
library(dplyr)
age_groupys <- group_by(pf,age)
pf.fc_by_age <- summarise(age_groupys,
          friend_count_mean=mean(friend_count),
          friend_count_median=median(friend_count),
          n=n())
pf.fc_by_age <- arrange(pf.fc_by_age)

p1<- ggplot(aes(x=age, y=friend_count_mean),
            data=subset(pf.fc_by_age, age<71))+
  geom_line()+
  geom_smooth()

p2<- ggplot(aes(x=age_with_month,y=friend_count_mean),
            data=subset(pf.fc_by_age_months, age_with_month<71))+
  geom_line()+
  geom_smooth()

p3<- ggplot(aes(x=round(age/5)*5,y=friend_count),
            data=subset(pf,age<71))+
  geom_line(stat = 'summary', fun.y=mean)

library(gridExtra)
grid.arrange(p1,p2,p3, ncol=1)
  

```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

